---
name: Chi Chin Christy
surname: Choi
position: ""
pronouns: she/her
address: "London, Hong Kong"
www: christychoicc.github.io
email: "choichichinchristy@gmail.com"
github: christychoicc
linkedin: choichichinchristy
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me

A Graduate Transport Planner at Stantec, with expertise in spatial data analytics, GIS and QUANT. I hold an MSc from the Bartlett, University College London (UCL) and a BSc from the University of Manchester. I am experienced in processing and analysing complex datasets, producing clear visualisation, and translating findings into evidence-based recommendations. I am committed to applying digital urban analytics in navigating complexities and delivering well-informed and inclusive long-term solutions to address challenges.

# Education

```{r}
library(dplyr)
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Details, 
  "Master of Science - MSc, Urban Spatial Science", "2025-2026", "University College London, Bartlett Centre for Advanced Spatial Analysis (CASA)", "London, U.K.", "Royal Geographical Society (with IBG) Accredited",
  "Master of Science - MSc, Urban Spatial Science", "2025-2026", "University College London, Bartlett Centre for Advanced Spatial Analysis (CASA)", "London, U.K.", "Dissertation: Assessing Spatial Equity in Multimodal Accessibility to Cooling-Effective Urban Green Spaces, A Case Study of London",
  "Master of Science - MSc, Urban Spatial Science", "2025-2026", "University College London, Bartlett Centre for Advanced Spatial Analysis (CASA)", "London, U.K.", "Specialisation in Big Data, Urban Modelling and Simulation: Urban Systems Theory; Geographic Information Systems and Science; Quantitative Methods; Foundations of Spatial Data Science; Data Science for Spatial Systems; Agent-based Modelling for Spatial Systems; Building Spatial Applications with Big Data; Remotely Sensing Cities and Environments.",
  
  "Bachelor of Science - BSc, Planning and Real Estate", "2022-2025", "University of Manchester", "Manchester, U.K.", "RICS Accredited, RTPI (Spatial) Partially Accredited", 
  "Bachelor of Science - BSc, Planning and Real Estate", "2022-2025", "University of Manchester", "Manchester, U.K.", "Second Class with Honours, Division One (2.1)", 
  "Bachelor of Science - BSc, Planning and Real Estate", "2022-2025", "University of Manchester", "Manchester, U.K.", "Dissertation: Explore The Role of Vertical Greenery Systems in Enhancing Urban Energy Efficiency in Dense Urban Areas, Strategies for Hong Kong.", 
  "Bachelor of Science - BSc, Planning and Real Estate", "2022-2025", "University of Manchester", "Manchester, U.K.", "Developed a strong understanding in urban theories, policies and application of planning law principles to real world case studies. Gained practical experiences in valuation and appraisal analyses, plan-making, and applied development projects incorporating spatial analyses, developed data analytics skills to support evidence-based decision-making approaches in urban design and research.", 
  
  "Global Summer School", "2022", "Tsinghua University", "China", "Subject Theme: A Healthy Planet for Sustainable Development",
  "Global Summer School", "2022", "Tsinghua University", "China", "Understanding challenges and propose solutions utilising AI in achieving digital inclusion for sign language users, implementing AI to promote inclusivity for all.",
  
  "A-Levels & GCSEs", "2017-2022", "St. Mary's School, Calne", "U.K.", "A-Levels: Fine Art, Mathematics, Economics, Chinese (Traditional Chinese, Mandarin)",
  "A-Levels & GCSEs", "2017-2022", "St. Mary's School, Calne", "U.K.", "EPQ: Extended Project (Level 3) Qualifications 2022",
  "A-Levels & GCSEs", "2017-2022", "St. Mary's School, Calne", "U.K.", "Young Enterprise West England 2021- Best Innovation Award, Best Presentation Award, Best Report Award, Best Overall Award",
  "A-Levels & GCSEs", "2017-2022", "St. Mary's School, Calne", "U.K.", "GCSE: English Language, English Literature, Mathematics, Double Award in Science, Fine Art, Geography, German Language, Religious Studies",
  "A-Levels & GCSEs", "2017-2022", "St. Mary's School, Calne", "U.K.", "University of Oxford German Olympiad Award 2019 – Highly Commended",
  
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Details
  )
```

# Experience

```{r}
tribble(
  ~Role, ~Year, ~Company, ~Where, ~Details,
  "Graduate Transport Planner", "October 2026-Present", "Stantec", "London, U.K.", "Transport and digital planning",
  
  "Operation Assistant, Internship", "July 2023 - August 2023", "Pacific Infrastructure Limited", "Hong Kong", "Assisted in the transition prior to the HKeToll system (smart mobility initiative for automated toll payments), monitoring CCTV footages for evasions, tracing vehicle owners and preparation of formal correspondence to ensure regulatory compliances.",
  
  "Retail Sales Specialist, Part-Time", "May 2023 - June 2023", "Croyaki Tea, Manchester", "Manchester, U.K.", "Delivered high quality customer services in managing transactions, assisting beverage production.", 
  
  "Landscape Architecture Summer Trainee", "July 2021 - August 2021", "Sanfield (Management) Ltd., SHKP Sun Hung Kai Properties", "Hong Kong", "Assisted in material selection, planning and execution of landscape projects, on site showroom preparation for Central Peak property development.",
  "Landscape Architecture Summer Trainee", "July 2021 - August 2021", "Sanfield (Management) Ltd., SHKP Sun Hung Kai Properties", "Hong Kong","Conducted a design project for a public park redevelopment (internship department assessment), translation of design concepts into practical solutions, using Auto CAD, Sketchup and Photoshop.",
  
  "Design Assistant, Internship", "July 2020 - August 2020", "GYSO Pearls & Jewellery Limited", "Hong Kong", "Managed showroom materials, photoshop edits for marketing visuals.",
) %>%
  detailed_entries(
    what = Role,
    when = Year,
    with = Company,
    where = Where,
    why = Details
  )
```

# Skills and Achievements

```{r technical-skills, echo=FALSE, results='asis'}
cat(
  "\\vspace{\\acvSectionContentTopSkip}\n",
  "\\cvsimpleentry{Technical Proficiency}{Python; R; SQL; QGIS; ArcGIS Pro; Google Earth Engine; SNAP; Git; GitHub; NetLogo; Adobe Photoshop; Illustrator}\n",
  sep = ""
)
```

```{r languages, echo=FALSE, results='asis'}
cat(
  "\\cvsimpleentry{Languages}{English; Cantonese; Mandarin; German (Intermediate Level)}\n"
)
```

```{r qualifications, echo=FALSE, results='asis'}
cat("\\entrytitlestyle{Qualifications}\n\n")

tribble(
  ~Qualification, ~Year,
  "Royal Academy of Dramatic Arts (RADA) Advanced Communication Course", "2021",
  "BCS ECDL Level 2 IT User Skills", "2020",
  "Duke of Edinburgh Bronze Award", "2019"
) %>%
  brief_entries(
    what = Qualification,
    when = Year
  )
```

```{r volunteer, echo=FALSE, results='asis'}
cat(
  "\\cvsimpleentry{Volunteer}{Agency for Volunteer Service Hong Kong -- Volunteer Member\\newline Crossroads Foundation -- Crossroads' Global Distribution -- Computer Department, AVS Miracle Summer Programme 2024}\n"
)
```

```{r interests, echo=FALSE, results='asis'}
cat(
  "\\cvsimpleentry{Interests / Hobbies}{Tennis; Running; Hiking; Pilates; Painting; Baking; Travelling}\n"
)
```
